### 2022-01-05 paper/paper.tex
visualization of IC and mesh for PID runs

For the problem setup we consider a periodic box of the domain $[-1,1]^3$ with four elements in each
spatial direction. This results in $64 (\text{\lstinline{polydeg}}+1)^3$ degrees
of freedom (DG nodes) when polynomials of degree \lstinline{polydeg} are used.
To make the mesh curvilinear, the interior of the box is heavily warped
by a combination of sine and cosine functions~\cite{chan2019efficient}. To integrate up to the
final time $T=1.0$, both codes use the five-stage, fourth-order low-storage explicit
Runge-Kutta method of Carpenter and Kennedy~\cite{CarpenterKennedy1994}.
A stable explicit time step is adaptively computed according to the local maximum wave
speed, the relative grid size, and an adjustable Courant-Friedrichs-Lewy (CFL)
coefficient $\text{CFL}\in(0,1]$~\cite{gassner2011}. For the performance computations presented herein
we fix this coefficient to be $\text{CFL}=0.5$.

We compare the performance of FLUXO and \trixi for two smooth nonlinear problems,
a manufactured solution for the 3D compressible Euler equations and Alfv\'{e}n wave propagation for
the 3D ideal magnetohydrodynamics (MHD) equations~\cite{gassner2009,altmann2012}. These initial conditions, available in FLUXO and
\trixi, are typically used to demonstrate the high-order accuracy and convergence properties
of the frameworks.

>>>>

For the problem setup we consider a periodic box of the domain $[-1,1]^3$ with four elements in each
spatial direction. This results in $64 (\text{\lstinline{polydeg}}+1)^3$ degrees
of freedom (DG nodes) when polynomials of degree \lstinline{polydeg} are used.
To make the mesh curvilinear, the interior of the box is heavily warped by
a mapping adapted from \cite{chan2019efficient}.
Specifically, we map Cartesian reference coordinates $(\xi, \eta, \zeta)$ to
physical coordinates $(x, y, z)$ via the transformation
\begin{equation}
\begin{aligned}
  y &= \eta  + 0.15 \bigl( \cos(1.5 \pi \xi) \cos(0.5 \pi \eta) \cos(0.5 \pi \zeta) \bigr),
  \\
  x &= \xi   + 0.15 \bigl( \cos(0.5 \pi \xi) \cos(2 \pi y) \cos(0.5 \pi \zeta) \bigr),
  \\
  z &= \zeta + 0.15 \bigl( \cos(0.5 \pi x) \cos(\pi y) \cos(0.5 \pi \zeta) \bigr).
\end{aligned}
\end{equation}
To integrate up to the
final time $T=1.0$, both codes use the five-stage, fourth-order low-storage explicit
Runge-Kutta method of Carpenter and Kennedy~\cite{CarpenterKennedy1994}.
A stable explicit time step is adaptively computed according to the local maximum wave
speed, the relative grid size, and an adjustable Courant-Friedrichs-Lewy (CFL)
coefficient $\text{CFL}\in(0,1]$~\cite{gassner2011}. For the performance computations presented herein
we fix this coefficient to be $\text{CFL}=0.5$.

We compare the performance of FLUXO and \trixi for two smooth nonlinear problems,
a manufactured solution for the 3D compressible Euler equations and Alfv\'{e}n wave propagation for
the 3D ideal magnetohydrodynamics (MHD) equations~\cite{gassner2009,altmann2012}. These initial conditions, available in FLUXO and
\trixi, are typically used to demonstrate the high-order accuracy and convergence properties
of the frameworks.
The curved mesh and the initial density for the compressible Euler problem are
visualized in Figure~\ref{fig:pid_euler_mesh}.

\begin{figure}[!h]
  \includegraphics[width=\linewidth]{../figures/pid_euler_mesh}
  \caption{Initial density of the compressible Euler problem on the curved mesh
           used for the performance benchmarks.}
  \label{fig:pid_euler_mesh}
\end{figure}
